### 2023-06-26 manuscript.tex
more pandoc [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/4b65e98117b1d8009b403ace5f9174d4e25dec32.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/4b65e98117b1d8009b403ace5f9174d4e25dec32/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5381409955

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/1fa38a4c54cf973f779ddf5f0320fe35cb36674f/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/1fa38a4c54cf973f779ddf5f0320fe35cb36674f}{stain/2022-fdo-paper@1fa38a4}
on June 26, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/4b65e98117b1d8009b403ace5f9174d4e25dec32/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/4b65e98117b1d8009b403ace5f9174d4e25dec32}{stain/2022-fdo-paper@4b65e98}
on June 26, 2023.
